### 2017-01-20 doc/manual/version3/inputParameters.tex
small update

\param{VMECRadialOption}
{integer}
{1}
{Only when \parlink{geometryScheme} == 5, 11 or 12.}
{Controls whether the nearest available flux surface in the {\ttfamily
    vmec wout} file or .bc file is used, or whether radial interpolation is applied to the data
to obtain the magnetic field components on the exact surface requested.\\

@@

{\ttfamily VMECRadialOption}=1: Use a surface that may be slightly
different from {\ttfamily XXX\_wish} to get the nearest available flux
surface from \vmec's HALF grid (or the .bc file grid).  
   The components of $\vect{B}$ in \vmec~are stored on the half grid, so interpolation is then unnecessary.\\

>>>>

\param{VMECRadialOption}
{integer}
{1}
{Only when \parlink{geometryScheme} == 5, 11 or 12.}
{Controls whether the nearest available flux surface in the {\ttfamily
    vmec wout} file or {\ttfamily .bc} file is used, or whether radial interpolation is applied to the data
to obtain the magnetic field components on the exact surface requested.\\

@@

{\ttfamily VMECRadialOption}=1: Use a surface that may be slightly
different from {\ttfamily XXX\_wish} to get the nearest available flux
surface from \vmec's HALF grid (or the {\ttfamily .bc} file grid).  
   The components of $\vect{B}$ in \vmec~are stored on the half grid, so interpolation is then unnecessary.\\
